Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-12-05 2016-Weak-FH-Bisim/WeakBisim.tex
add comment Fig.1

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium. \TODO{Decrire syntaxe graphique}

>>>>

Fig. \ref{SimpleProt:Spec} (right) shows a graphical view of the pNet of the system \emph{specification}:
the full system should be equivalent (e.g. through weak bisimulation)
to the two processes connected simply through a perfect medium. \TODO{ 
The pNet has a tree-like structure.  The root node of the tree {\it SimpleSystemSpec} is the top level of the pNet structure. It acts
as the parallel operator. It consists of tree nodes: two Holes $P$ and $Q$ and one subnet, noted {\it PrefectMedium}. Nodes of the tree are synchronized using four synchronization vectors, that  express the possible synchronization between the parameterized actions of a subset of the nodes. For instance, in the vector "$< p\_send(m),in(m),\_> \rightarrow \underline{in(m)}$ both $P$ and {\it PrefectMedium} nodes are involved in the synchronization. In particular, this means the synchronization between these processes occurs when  process $P$  performs $p\_send(m)$  action sending a message, and  the medium accepts the message through $in(m)$ action  at the same time. And the result that will be returned at upper level is the internal action  $\underline{in(m)}$.
}
